%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

  % Cinefly Internship
  \cventry
    {Software Developer} % Job title
    {Cinefly} % Organization
    {Gold Coast, Australia - Remote} % Location
    {Aug. 2023 - Present} % Date(s)
    {
  \begin{cvitems} % Description(s) of tasks/responsibilities
    \item {Focused on feature map development, utilizing tools such as Mapplic to enhance user interactivity and experience.}
    \item {Addressed and resolved challenges related to map functionalities, including story bubbles UI, zoom-in/zoom-out, and data conversion from CSV to JSON.}
    \item {Initiated the transformation of static case study maps to dynamic JSON formats, optimizing the frontend display.}
    \item {Collaborated with team members using Git for version control, frequently engaging in merge, pull request, rebase operations and gaining a comprehensive understanding of collaborative software development workflows.}
    \item {Worked on developing and maintaining software using technologies like Agile, JavaScript, HTML, CSS, TypeScript, Git, React.js, Redux.js, and SASS.}
  \end{cvitems}
}

    
  % SSG Internship
  \cventry
    {SSG Intern-SFL (STEM, Roster Development)} % Job title
    {Queensland University of Technology} % Organization
    {Brisbane, Australia - On-site} % Location
    {Jul. 2023 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Orchestrating the development of a full-stack application utilizing ASP.NET Core and Entity Framework.}
        \item {Leading the mission to create a comprehensive platform tailored for students participating in Peer Learning Facilitator (PLF) programs.}
        \item {Designing and implementing streamlined processes for roster signing and shift logging within the application.}
        \item {Leveraging the synergy between ASP.NET Core and SQL Server to ensure data integrity and efficient data management.}
        \item {Utilizing Bitbucket for version control to foster seamless collaboration within the development team.}
        \item {Contributing to a dynamic tool that significantly enhanced efficiency and engagement for both students and the PLF program.}
      \end{cvitems}
    }
    
  % FoS Marketing Student Ambassador
  \cventry
    {FoS Marketing Student Ambassador} % Job title
    {} % Organization
    {} % Location
    {Jul. 2023 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Worked as a student ambassador representing and promoting the Faculty of Science at QUT.}
        % ... Add other responsibilities or notable achievements if you have any ...
      \end{cvitems}
    }
    
  % Accommodation Assistant
  \cventry
    {Accommodation Assistant} % Job title
    {} % Organization
    {} % Location
    {Jun. 2023 - Aug. 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Assisted students with accommodation-related queries and managed bookings.}
        \item {Ensured smooth operations and addressed any issues related to student accommodations.}
        % ... Add other responsibilities or notable achievements if you have any ...
      \end{cvitems}
    }
     % Pushys Online Pty Ltd Position
  \cventry
    {IT SUPPORT OFFICE} % Job title
    {Pushys Online Pty Ltd} % Organization
    {Brisbane, Australia - On-site} % Location
    {Jul. 2022 - Nov. 2022} % Date(s)
    {
      \begin{cvitems} 
        \item {Technical Support and Administration: Provided comprehensive technical support for Pushys.com.au and BikeBug.com brands. Supported head office, warehouse, and retail stores, ensuring seamless operations. Administered and supported Magento 2 Enterprise, Neto/Maropost, and Netsuite/TCS POS systems. Managed Celigo iPaaS administration and Google Workspace administration.}
        \item {E-commerce and Marketing Support: Setup and managed online marketing promotions within e-commerce systems. Assisted in checking EDMs (Email Direct Marketing) before sending. Supported marketing systems like Klaviyo and Yotpo to enhance customer engagement.}
        \item {Warehouse and Inventory Management: Provided essential support for the Navigator WMS (Warehouse Management System), including Honeywell Voice Picking (Vocollect) implementation. Ensured efficient administration of Netsuite/TCS POS.}
        \item {Technical Infrastructure: Took charge of IT Networking tasks, managing data cabinets, servers, security camera systems, computers, and various devices. Supported both Windows 10/11 and Mac OS environments, including Miradore MDM.}
      \end{cvitems}
    }

  


\end{cventries}
